foreground detection via Deep Variation Transformation

### 2018-08-24 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.
 On branch master
 Changes to be committed:
	modified:   draft.aux
	modified:   draft.log
	modified:   draft.pdf
	modified:   draft.tex
	new file:   draft_with_comments_2018_08_24.pdf

%GMM 
% Ren:这里你说over time 不专业，但是论文里用得挺多的啊，表示随时间推移。还有那一句 pixels are .... to be if there exists ....， 我也是在其他论文里借过来用的。i
% 原文是Incoming pixels from video frames are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound. 
% cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods,
% 注意英语和汉语的表达习惯
% The most popular pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, 
which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel in time sequence.
%over time. 
Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence. 
%GMM+i
Moreover,
Zivkovic et al.\ \cite{Zivkovic2004} improve the GMM method with the utilization of recursive equation
to automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
%
% Ren: 这里你说看不懂，我的意思是想说，GMM+里面参数会自动更新。并且每一个像素位置的高斯个数也会自适应调整。原文里说的是： Recursive equations are used to constantly update the parameters and but also to simultaneously select the appropriate number of components for each pixel.
% An improved GMM method is introduced by Zivkovic\cite{Zivkovic2004} with the utilization of recursive equations, 
% which can 
% automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
%
%codebook
%Another popular algorithm in pixel based category is based on the Codebook. 
%Ren: 干脆删掉这一句了。。。
%Ren: 下面也重新写了。
Hence, Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.  
Then incoming pixels are compared with these codewords to see if their distances lies within a certain bound.

>>>>

%GMM 
% Ren:这里你说over time 不专业，但是论文里用得挺多的啊，表示随时间推移。还有那一句 pixels are .... to be if there exists ....， 我也是在其他论文里借过来用的。i
% 原文是Incoming pixels from video frames are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound. 
% cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods.
% 注意英语和汉语的表达习惯
% The most popular pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, 
It utilizes a mixture of weighted Gaussians to model the probability distribution of each pixel in time sequence.
%over time. 
Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence. 
%GMM+i
Moreover,
Zivkovic et al.\ \cite{Zivkovic2004} improve the GMM method with the utilization of recursive equation
to automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
%
% Ren: 这里你说看不懂，我的意思是想说，GMM+里面参数会自动更新。并且每一个像素位置的高斯个数也会自适应调整。原文里说的是： Recursive equations are used to constantly update the parameters and but also to simultaneously select the appropriate number of components for each pixel.
% An improved GMM method is introduced by Zivkovic\cite{Zivkovic2004} with the utilization of recursive equations, 
% which can 
% automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
%
%codebook
%Another popular algorithm in pixel based category is based on the Codebook. 
%Ren: 干脆删掉这一句了。。。
%Ren: 下面也重新写了。
Hence, Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.
The incoming pixels are compared with these codewords to see if their distances lies within a certain bound.
